An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/motiv.tex
a little progress
config: fix

\para{Example~4: Singular Value Errors} 
This should be the singular value error.
We need an example from Stack Overflow to illustrate the 
real-world problem. I guess the buffer size example is fine.}

>>>>

\para{Example~4: Singular Value Errors} 
A common error is that a value is set too high or too low.
For example, consider the following:
This should be the singular value error.
We need an example from Stack Overflow to illustrate the 
real-world problem. I guess the buffer size example is fine.
